Sketch Recognition and Understanding

### 2009-08-02 draft/System.tex

\section{Classification}%%Feature Set
\label{sec:Classification}
The system uses support vector machine (SVM) classifier with Linear kernel (Linear kernel) \cite{libsvm}. SVM is a binary classifier that maximizes the margin between the decision boundary and the support vectors. To enable SVM to learn multi classes we used one versus one strategy for combining set of binary classifier. This strategy trains $ \frac{n(n-1)}{{2}}$ binary classifier each distinguish between only two shapes. The final result is based on a number of votes each shape has from all classifiers. We used the library implementation of LibSVM \cite{libsvm} and its implementation of the one-vs-one strategy.
\subsection{Support Vector Machines}

% whate is support vector machines 
% how decisions is made
%  how training is done 
% how testing is donel. 
% kernels 
% how multi classifier are implemented 
% how parameter for cost is measured. 
% advantages 
% disadavantages 
% importance and applications used in it.

%Support vector machines (SVMs) are a set of related supervised learning methods used for classification and regression. Viewing input data as two sets of vectors in an n-dimensional space, an SVM will construct a separating hyperplane in that space, one which maximizes the margin between the two data sets. To calculate the margin, two parallel hyperplanes are constructed, one on each side of the separating hyperplane, which are "pushed up against" the two data sets. Intuitively, a good separation is achieved by the hyperplane that has the largest distance to the neighboring datapoints of both classes, since in general the larger the margin the lower the generalization error of the classifier.

%Support Vector Machines are based on the concept of decision planes that define decision boundaries. A decision plane is one that separates between a set of objects having different class memberships. A schematic example is shown in the illustration below. In this example, the objects belong either to class GREEN or RED. The separating line defines a boundary on the right side of which all objects are GREEN and to the left of which all objects are RED. Any new object (white circle) falling to the right is labeled, i.e., classified, as GREEN (or classified as RED should it fall to the left of the separating line).

@@

>>>>

\section{Classification}%%Feature Set
\label{sec:Classification}
The system uses support vector machine (SVM) classifier with Linear kernel (Linear kernel) \cite{libsvm}. SVM is a binary classifier that maximizes the margin between the decision boundary and the support vectors. To enable SVM to learn multi classes we used one versus one strategy for combining set of binary classifier. This strategy trains $ \frac{n(n-1)}{{2}}$ binary classifier each distinguish between only two shapes. The final result is based on a number of votes each shape has from all classifiers. We used the library implementation of LibSVM \cite{libsvm} and its implementation of the one-vs-one strategy.

\subsection{Support Vector Machines}

The foundation of Support Vector Machines (SVM) were developed by Vapnik \cite{} in 1995. It is gainig increase popularity due to the high performance and efficient implementation. The goal of SVM algorithms is to generate a sperating plane between two different classes which are represented using a set of n-dimentional vectors. The generated plane is used as a good classifier to the unseen exmaples. However, there can be more than one plane that can separates the data therefore SVM attempts to find the plane that maximize the margin (distance between classifier and nearest sample) between the two classes \ref{}. To calcuate the margin, two different hyperplanes are constructed, one plane on each side of the data, these two planes are then moved to generenate the maximum margin possilbe.

%The foundations of Support Vector Machines (SVM) have

% whate is support vector machines 
The classification problem can be restricted to consideration of the two-class problem
without loss of generality. In this problem the goal is to separate the two classes by a
function which is induced from available examples. The goal is to produce a classifier
that will work well on unseen examples, i.e. it generalises well. Consider the example
in Figure 2.1. Here there are many possible linear classifiers that can separate the data,
but there is only one that maximises the margin (maximises the distance between it
and the nearest data point of each class). This linear classifier is termed the optimal
separating hyperplane. Intuitively, we would expect this boundary to generalise well as
opposed to the other possible boundaries.

Let $x_i$ , $i$ = $1.2 \dots,N$ , be the feature vectors of the training set, $X$ . These
belong to either of two classes that are linearly spereable $\omega_1=1$ and  $\omega_2=-1$.
The goal, is to design a hyperplane which solve the equation 
\begin{equation}
g(x) = \omega^{T} x + \omega g = 0
\label{eq:svmhyper}
\end{equation}

@@

% how decisions is made
%  how training is done 
% how testing is donel. 
% kernels 
% how multi classifier are implemented 
% how parameter for cost is measured. 
% advantages 
% disadavantages 
% importance and applications used in it.
